Deep Reinforcement Learning for Conservation Decisions

### 2022-07-06 manuscript/manuscript.Rmd
Adding doi link

We have created a github repository <https://github.com/boettiger-lab/rl-intro> that contains the code used to produce the figures herein.

>>>>

We have created a GitHub repository <https://github.com/boettiger-lab/rl-intro> that contains the code used to produce the figures herein. The DOI for this repo is <https://zenodo.org/badge/latestdoi/318358820>.
